---
title: "Iteration and Listcols"
author: 'Zachary Katz (UNI: zak2132)'
date: "11/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Define functions

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```


## Lists

```{r}
l = 
  list(
      vec_numeric = 5:8,
      vec_logical = c(TRUE, FALSE),
      summary = summary(rnorm(1000, mean = 5, sd = 3))
)

l[[1]]
l[[2]]
l[[3]]

l[["summary"]]
```

## List of normals

```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

mean_and_sd(list_norms[[1]])
mean_and_sd(list_norms[[2]])
mean_and_sd(list_norms[[3]])
mean_and_sd(list_norms[[4]])
```

## For loop

Let's use a for loop to iterate over my list of normals.

```{r}
# Create empty output list
output = vector("list", length = 4)

# I could in theory save each result one at a time to output elements, but this is not efficient
output[[1]] = mean_and_sd(list_norms[[1]])

# For loop instead
for (i in 1:4) {
  
  output[[i]] = mean_and_sd(list_norms[[i]])
                             
}

output

```

Let's use map instead:

```{r}
# Much clearer
output = map(list_norms, mean_and_sd)
output

# Suppose I want the summary stats instead
output = map(list_norms, summary)
output

# Or IQR only
output = map(list_norms, IQR)
output

# Return just median, collapsed into a nicer structure
output = map_dbl(list_norms, median)
output
```

## List columns

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"),
    norms = list_norms
  )

# Can still do normal df stuff; weird column, but still just a data frame
listcol_df %>% 
  filter(name == "a")

# Can still do normal df stuff; weird column, but still just a data frame
listcol_df %>% pull(name)
listcol_df %>% pull(norms)

# Create new column in same df containing mean and sd
listcol_df %>% 
  mutate(
    summaries = map(norms, mean_and_sd)
  )
```

## Nested data

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

weather_df
```

Nest data within location:

```{r}
weather_nested = nest(weather_df, data = date:tmin)

# Create three separate nested tibbles, one for each location
weather_nested %>% 
  pull(data)

# Fit a regression to how tmax is related to tmin for Central Park
lm(tmax ~ tmin, data = weather_nested$data[[1]])

# Can also do for 2nd and 3rd locations
lm(tmax ~ tmin, data = weather_nested$data[[2]])
lm(tmax ~ tmin, data = weather_nested$data[[3]])

# Write a quick function to fit linear regression
weather_lm = function(df) {
  
  lm(tmax ~ tmin, data = df)
  
}

# Check result
weather_lm(weather_nested$data[[1]])

# Let's iterate across locations instead:

# Can take weather nested list of data sets and map across for each one applying weather_lm
map(weather_nested$data, weather_lm)

# Or could add column to existing df
weather_nested %>% 
  mutate(
    lm_results = map(data, weather_lm)
  )
  
```

Note that we can also unnest:

```{r}
unnest(weather_nested, data)

# Can use pipes as well for nesting/unnesting
weather_nested %>% 
  unnest(data)
```

## Napoleon again

```{r}

# Wrote this function last class to get reviews / stars
read_page_reviews = function(url) {
  
  html = read_html(url)
  
  title = 
    html %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  text = 
    html %>%
    html_nodes(".review-data:nth-child(5)") %>%
    html_text()
  
  tibble(title, stars, text)
}

# Also last class read the five pages of reviews on the URLs
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="
vec_urls = str_c(url_base, 1:5)
```

First, can define a vector of URLs to act as an input, and then iterate over that vector using both a for loop and a map_df statement.

```{r}
output = vector("list", 5)

for (i in 1:5) {
  output[[i]] = read_page_reviews(vec_urls[[i]])
}

dynamite_reviews = bind_rows(output)

# Map function is much cleaner
dynamite_reviews = map_df(vec_urls, read_page_reviews)
```

Can also do it this way to add to df containing original list of urls:

```{r}
dynamite_reviews = 
  tibble(
    page = 1:5,
    urls = str_c(url_base, page)) %>% 
  mutate(reviews = map(urls, read_page_reviews)) %>% 
  unnest()

dynamite_reviews
```

