---
title: "Writing Functions"
author: 'Zachary Katz (UNI: zak2132)'
date: "11/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
library(p8105.datasets)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Z scores

```{r}
x_vec = rnorm(25, mean = 5, sd = 4)


z_scores = function(x) {
      
    z = (x - mean(x)) / sd(x)
    
    return(z)
}

z_scores(x = x_vec)

y_vec = rnorm(40, mean = 12, sd = .3)

z_scores(y_vec)
```

How great is this?

```{r error = TRUE}
z_scores(3)

z_scores(c("my", "name", "is", "zak"))

z_scores(mtcars)
```

Let's try again.

```{r error = TRUE}
z_scores = function(x) {
      
      if(!is.numeric(x)) {
            stop("x needs to be numeric")
      }
      
      if(length(x) < 3) {
            stop("x should have at least 3 numbers")
      }
      
      z = (x - mean(x)) / sd(x)
      
      return(z)
}

# Should break
z_scores(mtcars)

# Should work
z_scores(y_vec)
```

## Multiple outputs

```{r}
mean_and_sd = function(x) {
      
      if(!is.numeric(x)) {
            stop("x needs to be numeric")
      }
      
      if(length(x) < 3) {
            stop("x should have at least 3 numbers")
      }
      
      mean_x = mean(x)
      sd_x = sd(x)
      
      output_df = 
            tibble(
                  mean = mean_x,
                  sd = sd_x
            )
      
      return(output_df)
}

mean_and_sd(x_vec)
mean_and_sd(y_vec)
```


## Different sample sizes, means, sds

```{r}
sim_data = 
            tibble(
                  x = rnorm(n = 30, mean = 5, sd = 4)
            )
      
      sim_data %>% 
            summarize(
                  mean = mean(x),
                  sd = sd(x)
            )
```


Let's write a function that simulates data, computes the mean and sd.

```{r}
sim_mean_sd = function(n, mu, sigma) {
      
      # do checks on input
      
      sim_data = 
            tibble(
                  x = rnorm(n, mean = mu, sd = sigma)
            )
      
      sim_data %>% 
            summarize(
                  mean = mean(x),
                  sd = sd(x)
            )
}

sim_mean_sd(10000, 40, 3)

# Can set defaults
sim_mean_sd = function(n, mu = 5, sigma = 4) {
      
      # do checks on input
      
      sim_data = 
            tibble(
                  x = rnorm(n, mean = mu, sd = sigma)
            )
      
      sim_data %>% 
            summarize(
                  mean = mean(x),
                  sd = sd(x)
            )
}

sim_mean_sd(10000)

# Can also enter arguments out of order when named
sim_mean_sd(sigma = 5, mu = 4, n=10000)
```

## Revisit Napoleon Dynamite

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_elements(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_elements("#cm_cr-review_list .review-rating") %>%
  html_text()

review_text = 
  dynamite_html %>%
  html_elements(".review-text-content span") %>%
  html_text()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)

```

Okay, but there are lots of pages of reviews...

Let's write a function that gets reviews based on page URL.

```{r}
get_page_reviews = function(page_url) {
  
  page_html = read_html(page_url)

  review_titles = 
    page_html %>%
    html_elements(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    page_html %>%
    html_elements("#cm_cr-review_list .review-rating") %>%
    html_text()
  
  review_text = 
    page_html %>%
    html_elements(".review-text-content span") %>%
    html_text()
  
  reviews = tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
)
  
  return(reviews)
}


url1 = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"
url2 = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2"
get_page_reviews(url1)
get_page_reviews(url2)

base_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

urls = str_c(base_url, 1:5)

bind_rows(
  get_page_reviews(urls[1]),
  get_page_reviews(urls[2]),
  get_page_reviews(urls[3]),
  get_page_reviews(urls[4]),
  get_page_reviews(urls[5])
)
```

NOTE: on website, check out LOTR example.

You can also pass in a summary function as an argument:

```{r}
x_vec = rnorm(25, 0, 1)

my_summary = function(x, summ_func) {
  summ_func(x)
}

my_summary(x_vec, sd)
```

This could be particularly valuable for re-ordering.

Remember, too, that scoping can be complicated:

```{r}
f = function(x) {
  z = x + y
  z
}

x = 1
y = 2

f(x = y)
```



